---
title: "Lab1"
author: "Caio Vianna"
date: "1/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load

```{r}


library(tidyverse)
library(sf)
library(leaflet)
library(tmap)


```

2. Review:  reading, exploring, wrangling and visualizing data

a. Read in data
```{r}

wine <- read_csv("wine_data.csv")

```


b. Wrangling
```{r}

wine_new <- wine %>% 
  select(country, province, winery, region_1, points, price) %>% 
  rename(state = province) %>% 
  filter(state == "California" | state == "Oregon" | state == "Washington") %>% 
  mutate(ppd = points/price) %>% 
  arrange(-ppd)


```

c. Use group_by() and summarize() to find summary statistics by group
```{r}

wine_summary <- wine_new %>% 
  group_by(state) %>% 
  summarize(
    mean_ppd = mean(ppd, na.rm = TRUE),
    max_ppd = max(ppd, na.rm = TRUE)
  )


```

d. A few gg-graphics
```{r}

wine_hists <- ggplot(wine_new, aes(x = ppd)) +
  geom_histogram(aes(fill=state)) +
  facet_wrap(~state, scales = "free")

wine_hists

```

new graph: scatterplot graph of price vs. points, with color determined by state, adding a linear model trendline on top of it
```{r}

wine_points <- ggplot(wine_new, aes(x=price, y=points))+
  geom_point(aes(color = state), alpha = 0.5) +
 # geom_smooth(color = "black", method = "lm", se = FALSE) +
  scale_color_manual(values = c("royalblue", "mediumorchid1", "orange")) +
  facet_wrap(~state) +
  theme_light()


wine_points



```

2. California counties (spatial data) using sf

```{r}
ca_counties <- st_read(dsn = ".", layer = "CA_Counties_TIGER2016")

ca_land <- ca_counties %>% 
  select(NAME, ALAND)

ca_pop_inc <- read_csv("ca_pop_inc.csv") %>% 
  rename(NAME = COUNTY)

ca_df <- full_join(ca_land, ca_pop_inc) %>% 
  select(NAME, MedFamilyIncome)




```


d. Use geom_sf to make a map in ggplot

```{r}

ca_income <- ggplot(ca_df) +
  geom_sf(aes(fill = MedFamilyIncome))

ca_income

ca_df_transform <- st_transform(ca_df, crs = 4326)

leaflet(ca_df_transform) %>% 
  addTiles() %>% 
  addPolygons()

```


















